The hydra and the rooster

### 2020-07-26 latex/chapter-hydras.tex

\subsection{Formal definition of battles}

@@

\begin{Coqsrc}
Inductive battle (B:Battle) : nat -> Hydra -> nat -> Hydra -> Prop :=
| battle_1 : forall i h  h', battle_r   B i  h h' -> 
                            battle B i h (S i) h'
| battle_n : forall i h  j h' h'',  battle_r  B i h h''  ->
                                   battle B (S i) h'' j h'  ->
                                   battle B i h j h'.
\end{Coqsrc}

>>>>

\subsection{Big steps}

@@

\begin{Coqsrc}
Inductive battle (B:Battle) : nat -> Hydra -> nat -> Hydra -> Prop :=

| battle_1 : forall i h  h', battle_r   B i  h h' -> 
                            battle B i h (S i) h'
| battle_n : forall i h  j h' h'',  battle_r  B i h h''  ->
                                   battle B (S i) h'' j h'  ->
                                   battle B i h j h'.
\end{Coqsrc}

### 2020-07-26 latex/chapter-introduction.tex

\subsubsection*{Contributions are welcome}
\label{sec:orgheadline2}

>>>>

\subsubsection*{Contributions}
Many thanks to \'Evelyne Contejean and Florian Hatat for their contribution. \'Evelyne contributed libraries on the recusrive path ordering (\emph{rpo}) for proving the well-foundedness of our representation of $\epsilon_0$ and $\Gamma_0$.
Florian Hatat proved many useful lemmas on countable sets, which we used in our adaptation of Schütte's formalization of countable ordinals.

\label{sec:orgheadline2}

### 2020-07-26 latex/chapter-ks.tex

The next step of our development is to extend this relationship to
the order $<$ on $[0,\epsilon_0)$ on one side, and hydra fights on the other side.

\begin{Coqsrc}
Lemma path_to_fight alpha s beta :
  path_to  beta  s alpha -> nf alpha ->
  iota alpha -+-> iota beta.
\end{Coqsrc}

As a corollary, we are now able to transform any inequality $\beta<\alpha<\epsilon_0$ into a (free) fight.

\begin{Coqsrc}
Lemma LT_to_fight alpha beta :
    beta < alpha ->  iota alpha -+-> iota beta.
\end{Coqsrc}

>>>>

The next step of our development is to extend this relationship to
the order $<$ on $[0,\epsilon_0)$ on one side, and hydra battles on the other side.

\begin{Coqsrc}
Lemma path_to_battle alpha s beta :
  path_to  beta  s alpha -> nf alpha ->
  iota alpha -+-> iota beta.
\end{Coqsrc}

As a corollary, we are now able to transform any inequality $\beta<\alpha<\epsilon_0$ into a (free) battle.

\begin{Coqsrc}
Lemma LT_to_battle alpha beta :
    beta < alpha ->  iota alpha -+-> iota beta.
\end{Coqsrc}
